Viscous Transport in Eroding Porous Media

### 2019-06-14 docs/transport/erosion_transport.tex
do the result in transport paper

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is

has more jumps than the one in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. In Fig.~\ref{fig:Eroding100tort}(c) 
we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers and
draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. 
The maximum of $\tau$ is 1.2547 and the minimum is 1.0003.

>>>>

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. To understand the meaning of jump 
of $\tau$, we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
We also can get the idea why the maximum value of $\tau$ is smaller 
than the one in the case of 20 bodies . 
The most of the bodies in this case are smaller than those in the case of 20 bodies.
So when two neighboring trajectories are splitted on the left side by a smaller body they do not
travel as far as the two splitted by a bigger body do after they rejoin on the right side.
